Study of Higgs plus single top production using events with a same sign dimuon at the Large Hadron Collider

### 2019-11-20 tesis_hiram/Abstract/abstract.tex
fix bugs

% ************************** Thesis Abstract *****************************
% Use `abstract' as an option in the document class to print only the titlepage and the abstract.
\begin{center}
	\justifying
I present a study on the production of a Higgs boson plus a single top quark ($tH$) in same sign dimuon channel $\mu^\pm \mu^\pm$ using data published by the CMS experiment at CERN. By studying this
process I explore a Higgs production mechanism which has not yet been observed
experimentally. The expected sensitivity is estimated by using an Asimov dataset for 35.9 fb$^{-1}$ of proton-proton collisions and is extrapolated to the LHC high luminosity phase.
The sensivity is also studied for the model with inverted Yukawa coupling $k_t$=-1, where $k_t$ is the top-Higgs coupling parameter, for comparison with the Standard Model.
\end{center}

>>>>

% ************************** Thesis Abstract *****************************
% Use `abstract' as an option in the document class to print only the titlepage and the abstract.
%\begin{center}
%	\justifying
I present a study on the production of a Higgs boson plus a single top quark ($tH$) in same sign dimuon channel $\mu^\pm \mu^\pm$ using data published by the CMS experiment at CERN. By studying this
process I explore a Higgs production mechanism which has not yet been observed
experimentally. The expected sensitivity is estimated by using an Asimov dataset for 35.9 fb$^{-1}$ of proton-proton collisions and is extrapolated to the  high luminosity phase of the LHC (HL-LHC).
The sensivity is also studied for the model with inverted Yukawa coupling $k_t$=-1, where $k_t$ is the top-Higgs coupling parameter modifier, for comparison with the Standard Model.
%\end{center}

### 2019-11-20 tesis_hiram/Abstract/resumen.tex
fix bugs

%\renewcommand{\absnamepos}{empty} % originally center
\begin{center}
	\justifying
Presento un estudio sobre la producci\'on de un boson de Higgs y un top quark ($tH$) en un canal de 2 muones con el mismo signo $\mu^\pm \mu^\pm$ usando datos publicados por el experimento CMS en el CERN. Estudiando este proceso, se explora este mecanismo de producci\'on del boson de Higgs que a\'un no se ha detectado experimentalmente. La sensibilidad esperada es calculada usando un grupo de datos tipo Asimov para 35.9 fb$^{-1}$ para colisiones de prot\'on-prot\'on y esos datos son extrapolados a niveles altos de luminosidad, de acuerdo a la fase de alta luminosidad en el LHC. La sensibilidad de la se\~nal es tambi\'en estudiada para el modelo con un acoplamiento invertido de Yukawa $k_t$=-1, donde $k_t$ es el par\'ametro de acoplamiento de top-Higgs, para compararlo con el Modelo Est\'andar.
\end{center}

>>>>

%\renewcommand{\absnamepos}{empty} % originally center
%\begin{center}
%	\justifying
Presento un estudio sobre la producci\'on del boson de Higgs y un top quark ($tH$) en el canal de 2 muones con el mismo signo $\mu^\pm \mu^\pm$ usando datos publicados por el experimento CMS en el CERN.
Estudiando este proceso se explora este mecanismo de producci\'on del boson de Higgs que a\'un no se ha detectado experimentalmente.
La sensibilidad esperada es calculada usando  datos de tipo Asimov para 35.9 fb$^{-1}$ de colisiones de prot\'on-prot\'on y es extrapolada la fase de alta luminosidad del LHC (HL-LHC).
La sensibilidad de la se\~nal es tambi\'en estudiada para el modelo con acoplamiento de Yukawa invertido $k_t$=-1, donde $k_t$ es el modificador del par\'ametro de acoplamiento de top-Higgs, en comparaci\'on con el Modelo Est\'andar.
%\end{center}
